---
title: "t-SNE plot"
format: html
---

I (Alvin) ran the t-SNE in Python, but plotting is horrible… bringing it back into R for plotting.

```{r}
library(MASS)
library(tidyverse)
library(here)
library(glue)
library(ggrepel)
library(ggraph)
# library(udpipe)
library(igraph)
library(ggtext)

theme_set(theme_bw() +
            theme(panel.grid = element_blank(),
                  strip.background = element_blank()))
```

```{r}
df_tsne <- read_csv(here("data", "all_contexts_tsne.csv")) |> 
  mutate(Activity = factor(Activity) |> fct_infreq(),
         Locations = factor(Location) |> fct_infreq())
```

# Activities
```{r}
df_summary_activity <- df_tsne |> 
  group_by(Activity) |> 
  summarise(n = n()) |> 
  arrange(desc(n))
```

```{r}
df_tsne_drop_activity <- df_tsne |> 
  left_join(df_summary_activity, by = join_by(Activity)) |> 
  mutate(Activity = case_when(
    n < 5000 ~ "other",
    Activity == "sitting" ~ "other",
    Activity == "walking" ~ "other",
    .default = Activity
  ))
```

```{r}
# find densest region for each activity for label location
df_labels_activity <- df_tsne_drop_activity |> 
  filter(Activity != "other") |>
  group_by(Activity) |>
  group_modify(~ {
    dens <- kde2d(.x$tsne_x, .x$tsne_y, n = 100)
    dens_df <- as.data.frame(expand.grid(tsne_x = dens$x, tsne_y = dens$y))
    dens_df$density <- as.vector(dens$z)
    dens_df <- dens_df |> arrange(desc(density))
    top_point <- dens_df[1, ]
    tibble(tsne_x = top_point$tsne_x, tsne_y = top_point$tsne_y)
  }) |>
  ungroup()
# join back the original tsne coords and descriptions for the closest point
df_labels_activity_text <- df_labels_activity |> 
  rowwise() |> 
  mutate(nearest_idx = which.min((df_tsne_drop_activity$tsne_x - tsne_x)^2 + 
                                   (df_tsne_drop_activity$tsne_y - tsne_y)^2)) |> 
  ungroup() |> 
  mutate(tsne_x = df_tsne_drop_activity$tsne_x[nearest_idx],
         tsne_y = df_tsne_drop_activity$tsne_y[nearest_idx],
         # Activity = df_tsne_drop_activity$Activity[nearest_idx],
         description = df_tsne_drop_activity$`Video description`[nearest_idx])
df_labels_activity_fixed <- df_labels_activity_text |> 
  mutate(activity_fixed = Activity |> str_to_sentence() |> str_replace_all("tv", "TV"),
         # label = glue('bold("{activity_fixed}:")~"{description}"') |> 
         #   str_wrap(50) |> 
         #   str_replace_all("\n", "\"\n\"") |> 
         #   str_split("\n") |> 
         #   map(\(x) reduce(x, \(a, b) glue("atop({a}, {b})"))),
         label = glue("{activity_fixed}: \"{description}\"") |> 
           str_wrap(70))
```


```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  # geom_point(data = df_tsne_drop_activity |> filter(Activity == "other"), 
  #            size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_drop_activity |> filter(Activity != "other"), 
             size = .01, alpha = .05) +
  geom_label_repel(
    data = df_labels_activity |> filter(Activity != "other"),
    aes(label = Activity, col = Activity),
    size = 3,
    box.padding = 0.5,
    point.padding = 0.3,
    segment.size = 0.5,
    show.legend = FALSE,
    max.overlaps = Inf,
    force = 8,
    direction = "both"
  ) +
  labs(x = "t-SNE dimension 1",
       y = "t-SNE dimension 2") +
  theme(legend.position = "none") +
  # scale_colour_manual(values = c(
  #   c("#FAA43AFF", "#60BD68FF", "#F17CB0FF", "#B2912FFF", 
  #     "#F15854FF", "#5DA5DAFF", "#B276B2FF", "#DECF3FFF")
  # ))
  ggthemes::scale_colour_solarized()
```

```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  # geom_point(data = df_tsne_drop_activity |> filter(Activity == "other"), 
  #            size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_drop_activity |> filter(Activity != "other"), 
             size = .01, alpha = .05) +
  geom_label_repel(
    data = df_labels_activity_fixed |> filter(Activity != "other"),
    aes(label = label, col = Activity),
    size = 1.6,
    box.padding = 0.5,
    point.padding = 0.3,
    segment.size = 0.5,
    show.legend = FALSE,
    max.overlaps = Inf,
    force = 8,
    direction = "both",
    # parse = TRUE,
    seed = 44
  ) +
  # labs(x = "t-SNE dimension 1",
  #      y = "t-SNE dimension 2") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.border = element_blank()) +
  # scale_colour_manual(values = c(
  #   c("#FAA43AFF", "#60BD68FF", "#F17CB0FF", "#B2912FFF", 
  #     "#F15854FF", "#5DA5DAFF", "#B276B2FF", "#DECF3FFF")
  # ))
  ggthemes::scale_colour_solarized()
```

```{r}
ggplot(data = df_tsne_drop_activity |> filter(Activity != "other"),
       mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  # geom_point(data = df_tsne_drop_activity |> filter(Activity == "other"), 
  #            size = .01, alpha = .05, col = "#555555") +
  geom_point(size = .01, alpha = .05) +
  geom_label_repel(
    data = df_labels_activity_fixed |> filter(Activity != "other"),
    aes(label = label, col = Activity),
    # cooking, eating, exploring, looking at device, playing, reading, watching tv
    nudge_x = c(3, 2.5, 2, 2, -100, -2, -6),
    nudge_y = c(0, 1, 0, -6, 0, -1, -4),
    size = 1.6,
    box.padding = 0.5,
    point.padding = 0.3,
    segment.size = 0.5,
    show.legend = FALSE,
    max.overlaps = Inf,
    force = 90,
    direction = "both",
    seed = 42
  ) +
  # labs(x = "t-SNE dimension 1",
  #      y = "t-SNE dimension 2") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.border = element_blank()) +
  coord_cartesian(xlim = c(-180, 180)) +
  # scale_colour_manual(values = c(
  #   c("#FAA43AFF", "#60BD68FF", "#F17CB0FF", "#B2912FFF", 
  #     "#F15854FF", "#5DA5DAFF", "#B276B2FF", "#DECF3FFF")
  # ))
  ggthemes::scale_colour_solarized()
```

```{r}
df_labels_activity_pos <- df_labels_activity_fixed |> 
  # cleaning, cooking, eating, exploring, looking at device, playing, reading, watching tv
  mutate(tsne_x = c(190, 175, 50, 170, 100, -170, -70, -160),
         tsne_y = c(0, 90, 140, -100, -145, 100, -140, -100),
         label = glue("**{activity_fixed}:** \"{description}\""),
         label = case_when(
           Activity == "exploring" ~ str_wrap(label, 65),
           Activity == "cleaning" ~ str_wrap(label, 50),
           Activity == "cooking" ~ str_wrap(label, 60),
           .default = str_wrap(label, 70)
         ) |> 
           str_replace_all("\n", "<br>"))

df_lines <- df_labels_activity_fixed |> 
  filter(Activity != "other") |> 
  select(tsne_x, tsne_y, Activity) |> 
  left_join(df_labels_activity_pos |> 
              select(tsne_x_pos = tsne_x, 
                     tsne_y_pos = tsne_y, 
                     Activity), by = join_by(Activity))

ggplot(data = df_tsne_drop_activity |> filter(Activity != "other"),
       mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  geom_point(size = .01, alpha = .05) +
  geom_segment(data = df_lines,
               aes(xend = tsne_x_pos, yend = tsne_y_pos)) +
  geom_richtext(data = df_labels_activity_pos,
                aes(label = label),
                size = 1.8) +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.border = element_blank()) +
  coord_cartesian(xlim = c(-230, 230),
                  ylim = c(-150, 150)) +
  ggthemes::scale_colour_solarized()
```


```{r}
ggplot(data = df_tsne_drop_activity |> filter(Activity != "other"),
       mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  # geom_point(data = df_tsne_drop_activity |> filter(Activity == "other"), 
  #            size = .01, alpha = .05, col = "#555555") +
  geom_point(size = .01, alpha = .05) +
  geom_label_repel(
    data = df_labels_activity_fixed |> filter(Activity != "other"),
    aes(label = label, col = Activity),
    # cooking, eating, exploring, looking at device, playing, reading, watching tv
    nudge_x = 150 - df_labels_activity_fixed |> filter(Activity != "other") |> pull(tsne_x),
    nudge_y = c(27.5, 1, 27.5, 60, 20, -1, 15),
    size = 1.6,
    box.padding = 0.5,
    point.padding = 0.3,
    segment.size = 0.5,
    show.legend = FALSE,
    max.overlaps = Inf,
    force = 0,
    direction = "both",
    seed = 42,
    hjust = 0
  ) +
  # labs(x = "t-SNE dimension 1",
  #      y = "t-SNE dimension 2") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.border = element_blank()) +
  coord_cartesian(xlim = c(-110, 255)) +
  ggthemes::scale_colour_solarized()
```


Visualiser function
```{r}
inspect_activity <- function(activity, colour = "cornflowerblue") {
  ggplot(mapping = aes(x = tsne_x, y = tsne_y,
                       col = Activity)) +
    geom_point(data = df_tsne_drop_activity |> filter(Activity != activity), 
               size = .01, alpha = .05, col = "#555555") +
    geom_point(data = df_tsne_drop_activity |> filter(Activity == activity), 
               size = .01, alpha = .05, col = colour) +
    geom_label_repel(
      data = df_labels_activity |> filter(Activity == activity),
      aes(label = Activity, col = Activity),
      size = 3,
      box.padding = 0.5,
      point.padding = 0.3,
      segment.size = 0.5,
      show.legend = FALSE,
      max.overlaps = Inf,
      force = 8,
      direction = "both",
      col = colour
    ) +
    labs(x = "t-SNE dimension 1",
         y = "t-SNE dimension 2") +
    theme(legend.position = "none")
} 
```

```{r}
inspect_activity("watching tv")
```

## k-means
```{r}
set.seed(42)
kmc_reading <- df_tsne |> 
  filter(Activity == "reading") |> 
  dplyr::select(tsne_x, tsne_y) |> 
  kmeans(centers = 3)
df_tsne_reading <- df_tsne |>
  filter(Activity == "reading") |> 
  mutate(cluster = factor(kmc_reading$cluster))
```

```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y)) +
  geom_point(data = df_tsne_drop_activity |> filter(Activity != "reading"),
             size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_reading, mapping = aes(col = cluster),
             size = .01, alpha = .05) +
  labs(x = "t-SNE dimension 1",
       y = "t-SNE dimension 2") +
  theme(legend.position = "bottom") + 
  guides(colour = guide_legend(override.aes = list(alpha = 1)))
```

By manual inspection of videos, cluster 1 shows children reading while sitting in their caregivers' lap or by themselves (book appears in the bottom of the video); cluster 3 has caregivers reading to children but at a distance (book appears further away at the centre of the video); cluster 2 is more ambiguous with scenes that sometimes have books or paper but are less clearly instances of shared book reading.

```{r}
set.seed(42)
kmc_tv <- df_tsne |> 
  filter(Activity == "watching tv") |> 
  dplyr::select(tsne_x, tsne_y) |> 
  kmeans(centers = 3)
df_tsne_tv <- df_tsne |>
  filter(Activity == "watching tv") |> 
  mutate(cluster = factor(kmc_tv$cluster))
```

```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y)) +
  geom_point(data = df_tsne_drop_activity |> filter(Activity != "watching tv"),
             size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_tv, mapping = aes(col = cluster),
             size = .01, alpha = .05) +
  labs(x = "t-SNE dimension 1",
       y = "t-SNE dimension 2") +
  theme(legend.position = "bottom") + 
  guides(colour = guide_legend(override.aes = list(alpha = 1)))
```

This time the clusters seem more spurious. Clips from cluster 1 typically have watching a screen (TV/tablet) as a partial or background activity; cluster 2 has "a person watching TV" whereas cluster 3 has "a child watching TV" in the descriptions with no clear visual difference.

```{r}
set.seed(42)
kmc_playing <- df_tsne |> 
  filter(Activity == "playing") |> 
  dplyr::select(tsne_x, tsne_y) |> 
  kmeans(centers = 3)
df_tsne_playing <- df_tsne |>
  filter(Activity == "playing") |> 
  mutate(cluster = factor(kmc_playing$cluster))
```

```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y)) +
  geom_point(data = df_tsne_drop_activity |> filter(Activity != "playing"),
             size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_playing, mapping = aes(col = cluster),
             size = .01, alpha = .05) +
  labs(x = "t-SNE dimension 1",
       y = "t-SNE dimension 2") +
  theme(legend.position = "bottom") + 
  guides(colour = guide_legend(override.aes = list(alpha = 1)))
```

```{r}
set.seed(123)
df_labels_playing <- df_tsne_playing |> 
  group_by(Activity, cluster) |> 
  summarise(tsne_x = mean(tsne_x) + rnorm(1, 0, 5),
            tsne_y = mean(tsne_y) + rnorm(1, 0, 5),
            .groups = "drop") |> 
  ungroup()

df_labels_playing_text <- df_labels_playing |> 
  rowwise() |> 
  mutate(nearest_idx = which.min((df_tsne_drop_activity$tsne_x - tsne_x)^2 + 
                                   (df_tsne_drop_activity$tsne_y - tsne_y)^2)) |> 
  ungroup() |> 
  mutate(tsne_x = df_tsne_drop_activity$tsne_x[nearest_idx],
         tsne_y = df_tsne_drop_activity$tsne_y[nearest_idx],
         # Activity = df_tsne_drop_activity$Activity[nearest_idx],
         description = df_tsne_drop_activity$`Video description`[nearest_idx])
df_labels_playing_fixed <- df_labels_playing_text |> 
  mutate(activity_fixed = Activity |> str_to_sentence() |> str_replace_all("tv", "TV"),
         # label = glue('bold("{activity_fixed}:")~"{description}"') |> 
         #   str_wrap(50) |> 
         #   str_replace_all("\n", "\"\n\"") |> 
         #   str_split("\n") |> 
         #   map(\(x) reduce(x, \(a, b) glue("atop({a}, {b})"))),
         label = glue("{activity_fixed}: \"{description}\"") |> 
           str_wrap(70))
```

```{r new_plot}
df_labels_activity_pos_rep <- df_labels_activity_fixed |> 
  filter(Activity != "playing") |> 
  bind_rows(df_labels_playing_fixed) |> 
  # cleaning, cooking, eating, exploring, looking at device, reading, watching tv, playing x3
  mutate(tsne_x = c(190, 175, 50, 170, 100, -70, -160, -140, -180, -180),
         tsne_y = c(0, 90, 140, -100, -145, -140, -100, 125, 60, -50),
         label = glue("**{activity_fixed}:** \"{description}\""),
         label = case_when(
           Activity == "exploring" ~ str_wrap(label, 65),
           Activity == "cleaning" ~ str_wrap(label, 50),
           Activity == "cooking" ~ str_wrap(label, 60),
           Activity == "playing" ~ str_wrap(label, 60),
           .default = str_wrap(label, 70)
         ) |> 
           str_replace_all("\n", "<br>"))

df_lines_rep <- df_labels_activity_fixed |> 
  filter(Activity != "playing") |> 
  bind_rows(df_labels_playing_fixed) |>
  select(tsne_x, tsne_y, Activity) |> 
  cbind(df_labels_activity_pos_rep |> 
              select(tsne_x_pos = tsne_x, 
                     tsne_y_pos = tsne_y))

ggplot(data = df_tsne_drop_activity |> filter(Activity != "other"),
       mapping = aes(x = tsne_x, y = tsne_y,
             col = Activity)) +
  geom_point(size = .01, alpha = .05) +
  geom_segment(data = df_lines_rep,
               aes(xend = tsne_x_pos, yend = tsne_y_pos)) +
  geom_richtext(data = df_labels_activity_pos_rep,
                aes(label = label),
                size = 1.8) +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.border = element_blank()) +
  coord_cartesian(xlim = c(-230, 230),
                  ylim = c(-150, 150)) +
  ggthemes::scale_colour_solarized()
```


## Keywords
```{r eval=F}
udpipe_download_model("english-ewt")
ud_model <- udpipe_load_model("english-ewt-ud-2.5-191206.udpipe")

udpipe_annotate(ud_model, df_tsne$`Video description`)
```

Something crude as a first pass
```{r}
df_tokens <- df_tsne |> 
  mutate(words = `Video description` |> str_to_lower() |> 
           str_remove_all("[^a-z ]") |> str_split(" ")) |> 
  unnest(words)
df_tokens_summary <- df_tokens |> 
  group_by(Activity, words) |> 
  summarise(n = n(),
            .groups = "drop_last") |> 
  mutate(freq = n / sum(n)) |> 
  arrange(Activity, desc(freq))
df_tokens_overall <- df_tokens |> 
  group_by(words) |> 
  summarise(n = n(),
            .groups = "drop") |> 
  mutate(freq = n / sum(n))
df_tokens_excess <- df_tokens_summary |> 
  left_join(df_tokens_overall, by = join_by(words), 
            suffix = c("_activity", "_overall")) |> 
  mutate(excess = freq_activity - freq_overall) |> 
  arrange(Activity, desc(excess))
```


```{r}
KEYNESS_CORRECTION = 10

tokens_of_interest <- all_trans_annotated |> 
  group_by(token) |> 
  summarise(token_counts = n(),
            .groups = "drop") |>
  filter(token_counts >= 20 + KEYNESS_CORRECTION) |>
  pull(token)

locations_of_interest <- trans_by_loc |> 
  filter(!is.na(locations_avg)) |> 
  pull(locations_avg) |> 
  unique()

keyness <- map(locations_of_interest, \(loc) {
  foc <- trans_by_loc |> 
    filter(locations_avg == loc) |>
    pull(token) |> 
    ARF() |> 
    rename(arf_focal = ARF)
  ref <- trans_by_loc |> 
    filter(locations_avg != loc) |> 
    pull(token) |> 
    ARF() |> 
    rename(arf_reference = ARF)
  foc |> 
    left_join(ref, by = join_by(word)) |> 
    mutate(keyness = arf_focal / arf_reference) |> 
    rename(token = word) |> 
    mutate(location = loc)
}) |> list_rbind()
```


# Locations
```{r}
df_summary_location <- df_tsne |> 
  group_by(Location) |> 
  summarise(n = n()) |> 
  arrange(desc(n))
```

```{r}
df_tsne_drop_location <- df_tsne |> 
  left_join(df_summary_location, by = join_by(Location)) |> 
  mutate(Location = case_when(
    n < 1000 ~ "other",
    .default = Location
  ))
```

```{r}
df_labels_location <- df_tsne_drop_location |> 
  filter(Location != "other") |>
  group_by(Location) |>
  group_modify(~ {
    dens <- kde2d(.x$tsne_x, .x$tsne_y, n = 100)
    dens_df <- as.data.frame(expand.grid(tsne_x = dens$x, tsne_y = dens$y))
    dens_df$density <- as.vector(dens$z)
    dens_df <- dens_df |> arrange(desc(density))
    top_point <- dens_df[1, ]
    tibble(tsne_x = top_point$tsne_x, tsne_y = top_point$tsne_y)
  }) |>
  ungroup()
```


```{r}
ggplot(mapping = aes(x = tsne_x, y = tsne_y,
             col = Location)) +
  geom_point(data = df_tsne_drop_location |> filter(Location == "other"), 
             size = .01, alpha = .05, col = "#555555") +
  geom_point(data = df_tsne_drop_location |> filter(Location != "other"), 
             size = .01, alpha = .05) +
  geom_label_repel(
    data = df_labels_location |> filter(Location != "other"),
    aes(label = Location, col = Location),
    size = 3,
    box.padding = 0.5,
    point.padding = 0.3,
    segment.size = 0.5,
    show.legend = FALSE,
    max.overlaps = Inf,
    force = 8,
    direction = "both"
  ) +
  labs(x = "t-SNE dimension 1",
       y = "t-SNE dimension 2") +
  theme(legend.position = "none")
```

Visualiser function
```{r}
inspect_location <- function(location, colour = "cornflowerblue") {
  ggplot(mapping = aes(x = tsne_x, y = tsne_y,
                       col = Location)) +
    geom_point(data = df_tsne_drop_location |> filter(Location != location), 
               size = .01, alpha = .05, col = "#555555") +
    geom_point(data = df_tsne_drop_location |> filter(Location == location), 
               size = .01, alpha = .05, col = colour) +
    geom_label_repel(
      data = df_labels_location |> filter(Location == location),
      aes(label = Location, col = Location),
      size = 3,
      box.padding = 0.5,
      point.padding = 0.3,
      segment.size = 0.5,
      show.legend = FALSE,
      max.overlaps = Inf,
      force = 8,
      direction = "both",
      col = colour
    ) +
    labs(x = "t-SNE dimension 1",
         y = "t-SNE dimension 2") +
    theme(legend.position = "none")
} 
```

```{r}
inspect_location("hallway")
```

# Smoothing and network
```{r}
df_smooth <- df_tsne |> 
  mutate(video = video_id |> str_remove("_[0-9]+\\.mp4")) |> 
  group_by(video) |> 
  mutate(activity_lagged = lag(Activity),
         activity_leaded = lead(Activity),
         activity_smooth = case_when(
           activity_lagged == activity_leaded ~ activity_lagged,
           .default = Activity
         ),
         location_lagged = lag(Location),
         location_leaded = lead(Location),
         location_smooth = case_when(
           location_lagged == location_leaded ~ location_lagged,
           .default = Location
         ))
```

```{r}
# make an igraph, with edge weights as counts of transitions
activity_include <- df_summary_activity |>
  filter(n >= 5000) |>
  pull(Activity)

edges_activity <- df_smooth |>
  mutate(activity_smooth_next = lead(activity_smooth)) |> 
  ungroup() |> 
  count(activity_smooth, activity_smooth_next) |> 
  rename(from = activity_smooth,
         to = activity_smooth_next,
         weight = n)

edges_activity_include <- edges_activity |> 
  filter(from %in% activity_include,
         to %in% activity_include)

# graph_activity <- graph_from_data_frame(
#   edges_activity_include |> 
#     filter(!is.na(from), !is.na(to),
#            from != to),
#   directed = TRUE
# )

edges_activity_simplified <- edges_activity_include |> 
  mutate(from = as.character(from),
         to = as.character(to),
         node1 = pmin(from, to),
         node2 = pmax(from, to)) |> 
  group_by(node1, node2) |> 
  summarise(weight = sum(weight), .groups = 'drop') |> 
  rename(from = node1, to = node2)

nodes_activity_simplified <- df_smooth |> 
  mutate(activity_smooth_next = lead(activity_smooth)) |> 
  filter(activity_smooth != activity_smooth_next |
           is.na(activity_smooth_next)) |> 
  group_by(Activity) |> 
  summarise(n = n()) |> 
  filter(Activity %in% activity_include) |> 
  rename(name = Activity, size = n)

graph_activity_simplified <- graph_from_data_frame(
  edges_activity_simplified |> 
    filter(!is.na(from), !is.na(to),
           from != to),
  vertices = nodes_activity_simplified
)

# plot(graph_activity, 
#      edge.arrow.size = 0.2,
#      edge.width = E(graph_activity)$weight / 1000)
```


```{r}
set.seed(123)
ggraph(graph_activity_simplified, layout = 'fr') +
  geom_edge_link0(aes(width = weight/1000), 
                  # arrow = arrow(length = unit(2, 'mm')), 
                  # end_cap = circle(3, 'mm'),
                  alpha = 0.6,
                  color = "gray50") +
  geom_node_point(aes(size = size, col = name)) +
  geom_node_label(aes(label = name, col = name), 
                  repel = TRUE, 
                  size = 3.2) +
  scale_edge_width(range = c(0.2, 5), guide = "none") +
  theme_void() +
  theme(legend.position = "none") +
  scale_color_manual(values = c(
    "cleaning" = "#268bd2", "cooking" = "#b58900", "eating" = "#cb4b16",
    "exploring" = "#dc322f", "looking at device" = "#d33682", "playing" = "#6c71c4",
    "reading" = "#2aa198", "watching tv" = "#859900", "walking" = "#2eb354", "sitting" = "#2e49b3"
  ))
```



